---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## gardenr 
The goal of gardenr is provide simple functions of analyzing the data from Gardener's interneuron classification as well as to provide examples of analyses of such data.

## Installation
You can use the `devtools` package to install `gardenr` from Github. 
```{r, eval = FALSE}
devtools::install_github('ComputationalIntelligenceGroup/gardenr')
``` 

The user needs to provide the path to the folder containing the data. These can be downloaded from ...(TODO)
```{r}
folder <- '/home/bmihaljevic/code-gardener/gardener-experiment-data/data/' 
library(tidyverse)
```

## Usage
`garnenr` functions return the data for all 320 cells. There are functions for the classification labels `get_all_labels`, metadata `get_all_meta`, and alternative type names and definitions `get_alternative_types`.
```{r example}
library(gardenr)
annotations <- get_all_labels(folder ) 
summary(annotations)
``` 

```{r}
alternative <- get_alternative_types(folder)
summary(alternative)
```

```{r}
metadata <- get_all_meta(folder)
summary(metadata)
``` 

To get data on a specific cell or annotator, we only need filter by id:
```{r}
metadata %>% filter(neuron == 12)
head(annotations %>% filter(neuron == 12))
```

```{r} 
head(annotations %>% filter(annotator == 2))
alternative %>% filter(annotator == 2)
```

It is easy to combine the three data frames using joins, and then compute summaries with `tidyverse` functions. For example, the alternative type definition to an annotation
```{r}
head(left_join(annotations, alternative, by = c("other" = "type", "annotator" = "annotator"))) 
```    
The primary key in `alternative` consits of `annotator` and `type` and hence we need both in the join.
 
There is a utility function to return the counts for all categories, with a single entry per neuron.
```{r}
counts <- get_all_counts(folder) 
head(counts)
```

We can join the above with metadata to get thorough information for each cell. 
```{r}
meta_count <- left_join(counts, metadata, by = 'neuron') %>% select(-paper, -original.type, -archive, -neuromorpho.name)
head(meta_count)
```
There is a utility function doing just that:
```{r}
head(get_all_counts_meta(folder) )
```
  
These data are also available in a different format, which is a bit easier to analyze
```{r} 
annot_tidy <- make_annotations_tidy(annotations) 
head(annot_tidy )
``` 

## Examples  
 
- How many partially labelled cells?
```{r}
table(annotations$complete) 
``` 

- Get raw frequencies of the different categories
```{r}  
annot_tidy <- make_annotations_tidy(annotations) 
annot_tidy %>% group_by(feature, value) %>% tally()
# library(ggplot2)
ggplot(annot_tidy, aes(x = value, color = feature)) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
 
- Only consider cells with above > 30 neurocientists agreeing on a specific label
```{r} 
annot_tidy <- make_annotations_tidy(annotations) 
above30 <- annot_tidy %>% group_by(neuron, feature, value) %>% tally() %>% filter(n > 30)
above30 %>% group_by(feature) %>% summarize(n_distinct(neuron))  
```


- Restrict analysis to unrotated, monkey cells 
```{r}
monkey <- metadata %>% filter(species == 'Monkey')
counts <- get_all_counts_meta(folder)
counts %>% filter(species == 'Monkey') 
```  

### Alternative type names

- 27 out of 48 neuroscientists provided alternative type names for the cells 
```{r}
length(unique(alternative$annotator))
unique(alternative$annotator) 
```    

- How many alternative types per neuroscientist? How many other cells per neuroscientist?
```{r}
types <- alternative %>% group_by(annotator) %>% tally()
other <- annotations %>% group_by(annotator) %>% filter(F5 == 'other') %>% tally()
ggplot(data.frame(types = types$n, cells = other$n), aes(x = types, y = cells)) + geom_point()
```

- Words used in alternative types and definitions:
    - The most common word is `bitufted'
```{r} 
library(tidytext)
library(wordcloud)
alt <- alternative 
alt$type <- as.character(alternative$type ) 
alt <- alt %>% unnest_tokens(type, type)
alt %>%  count(type, sort = TRUE)      
alt %>%  count(type, sort = TRUE)      %>%  with(wordcloud(type, n, random.order = FALSE, max.words = 50 , colors= brewer.pal(8,"Dark2")))
```

```{r} 
alt <- alternative 
alt$definition <- as.character(alternative$definition )   
alt <- alt %>% unnest_tokens(definition, definition)
alt <- alt %>% anti_join(get_stopwords(), by = c("definition" = "word"))
alt %>%  count(definition, sort = TRUE)      
alt %>%  count(definition, sort = TRUE)      %>%  with(wordcloud(definition, n, random.order = FALSE, max.words = 50 , colors= brewer.pal(8,"Dark2")))
```  
