---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## gardenr 
The goal of gardenr is provide simple functions of analyzing the data from Gardener's interneuron classification as well as to provide examples of analyses of such data.

## Installation
You can use the `devtools` package to install `garnenr` from Github. 
```{r, eval = FALSE}
devtools::install_github('ComputationalIntelligenceGroup/gardenr')
``` 

The user needs to provide the path to the folder containing the data. These can be downloaded from ...(TODO)
```{r}
folder <- '/home/bmihaljevic/code-gardener/gardener-experiment-data/data/' 
library(tidyverse)
```

## Usage
`garnenr` functions return the data for all 320 cells. There are functions for the classification labels `get_all_labels`, metadata `get_all_meta`, and alternative type names and definitions `get_alternative_types`.
```{r example}
library(gardenr)
annotations <- get_all_labels(folder ) 
summary(annotations)
``` 

```{r}
alternative <- get_alternative_types(folder)
summary(alternative)
```

```{r}
metadata <- get_all_meta(folder)
summary(metadata)
``` 

To get data on a specific cell or annotator, we only need filter by id:
```{r}
metadata %>% filter(neuron == 12)
head(annotations %>% filter(neuron == 12))
```

```{r} 
head(annotations %>% filter(annotator == 2))
alternative %>% filter(annotator == 2)
```

It is easy to combine the three data frames using joins, and then compute summaries with `tidyverse` functions. For example, the alternative type definition to an annotation
```{r}
head(left_join(annotations, alternative, by = c("other" = "type", "annotator" = "annotator"))) 
```    
The primary key in `alternative` consits of `annotator` and `type` and hence we need both in the join.
 
There is a utility function to return the counts for all categories, with a single entry per neuron.
```{r}
counts <- get_all_counts(folder) 
head(counts)
```

We can join the above with metadata, to get a thorough information for each cell. 
```{r}
meta_count <- left_join(counts, metadata, by = 'neuron') %>% select(-paper, -original.type, -archive, -neuromorpho.name)
head(meta_count)
```
There is a utility function doing just that:
```{r}
head(get_all_counts_meta(folder) )
```



These data are also available in a different format, which is a bit easier to analyze
```{r}
# TODO
```


# Examples  



- Those which are other, and have this
- How many partially labelled cells?
- ... 
- Directly filter by confidence in some variable. Here, use the row verions. 

```{r}
other <- droplevels(subset(annotations, F5 == 'other'))
length(unique(other$annotator))   
```   

- Statistics for a species
   - we join, then filter

- 27 out of 48 neuroscientists provided alternative type names for the cells
```{r}
alternative <- get_alternative_types(folder)
head(alternative)
length(unique(alternative$annotator))
unique(alternative$annotator)
``` 

## Alternative type names
- Word cloud
- How many? Distribution per neuroscients
