---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# gardenr 
The goal of gardenr is to ... The user needs to provide the path to the folder containing the data. These can be downloaded from ...(TODO)

```{r}
folder <- '/home/bmihaljevic/code/gardener-experiment-data/data/' 
```


## Example

- `get_all_*` functions, the return data for all 320 cells
```{r example}
library(gardenr)
annotations <- get_all_labels(folder ) 
summary(annotations)
``` 

- 27 out of 48 neuroscientists provided alternative type names for the cells
```{r}
alternative <- get_alternative_types(folder)
head(alternative)
length(unique(alternative$annotator))
unique(alternative$annotator)
```
```{r}

```

We can easily map with the other data frame. **Those which are other, and have this.**
```{r}
other <- droplevels(subset(annotations, F5 == 'other'))
a <- levels(other$other) 
b <- levels(alternative$type)
setdiff(a, b)
setdiff(b, a)
library(tidyverse)
other <- left_join(other, alternative, by = c("other" = "type"))
length(unique(other$annotator)) 
```

```{r}

```

 
From here, it is easy to filter for a given cell, species, etc. 
Also, simple functions that work at cell level:



